hormones

### 2019-10-11 analysis/07_hormones.Rmd
new hormone figs

PETC %>% 
  filter(hormone == "testosterone", sex == "male")  %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = sex)) +
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  facet_wrap(~study, scales = "free_x") +
  labs(y = "Testosterone") +
  scale_fill_manual(values = c("#00BFC4"))
```

```{r estradiol}
PETC %>% 
  filter(hormone == "estradiol", sex == "female")  %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = sex)) +
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  facet_wrap(~study, scales = "free_x") +
  labs(y = "Estradiol (ng/mL)")

@@

```{r progesterone}
PETC %>% 
  filter(hormone == "progesterone")  %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = sex)) +
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  facet_wrap(~study, scales = "free_x") +
  labs(y = "Progesterone (ng/mL)") +
  ylim(c(0,6))

@@

```{r cort}

PETC %>% 
  filter(hormone == "cort")  %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = sex)) +
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  facet_wrap(~study, scales = "free_x") +
  labs(y = "Corticosterone (ng/mL)") +
  ylim(c(0,10))

@@

a <- ggplot(characterization, aes(x = treatment, y = `Prolactin ng/mL`, fill = sex)) +
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(subtitle = "Characterization", y = "Prolactin (ng/mL)", x = NULL) +
  #geom_text(data = df, aes(x,y, label = text), color = "darkgrey") +
      ylim(0,120) 
a

@@

e <- manipulation %>%
  ggplot( aes(x = treatment, y = `Prolactin ng/mL`)) +
    geom_boxplot(aes(fill = sex)) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "bottom",
          legend.title = element_blank()) +
    ylim(0,125) +
    labs(subtitle = "Manipulation",
       y = "Prolactin (ng/mL)", x = NULL)
e

@@

f <-  prolactin %>%
  filter(treatment %in% c("control", "bldg", "inc_d3", "M_inc3",
                          "inc_d9",  "M_inc9", "inc_d17","M_inc17",
                          "hatch", "M_n2")) %>%
ggplot(aes(x = treatment, y = `Prolactin ng/mL`, fill = Sex)) +
  geom_boxplot(aes(alpha = study)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none") +
  labs(subtitle = "Offspring removed",
       x = NULL) +
  facet_wrap(~sex) +
  annotate("rect", xmin = 2.5, xmax = 4.5, ymin = 0, ymax = 120, alpha = .2) +
    #annotate("rect", xmin = 4.5, xmax = 6.5, ymin = 0, ymax = 120, alpha = .3) +
    annotate("rect", xmin = 6.5, xmax = 8.5, ymin = 0, ymax = 120, alpha = .2) +
    #annotate("rect", xmin = 8.5, xmax = 10.5, ymin = 0, ymax = 120, alpha = .3) +
  ylim(0,120) +
  scale_alpha_manual(values = c(1,0.5))

g <-  prolactin %>%
  filter(treatment %in% c("early","prolong", "extend",
                          "inc_d9","inc_d17","hatch", "n5" )) %>% droplevels() %>%
ggplot(aes(x = treatment, y = `Prolactin ng/mL`, fill = Sex)) +
  geom_boxplot(aes(alpha = study)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none") +
  labs(subtitle = "Timing of transition altered",
       x = NULL, y = NULL) +
  facet_wrap(~sex) +
    annotate("rect", xmin = 4.5, xmax = 7.5, ymin = 0, ymax = 120, alpha = .3) +
  ylim(0,120) +
  scale_alpha_manual(values = c(1,0.5))

>>>>

PETC %>% 
  filter(hormone == "testosterone", sex == "male")  %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = sex)) +
  geom_boxplot() + geom_jitter() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  facet_wrap(~study, scales = "free_x") +
  labs(y = "Testosterone") +
  scale_fill_manual(values = c("#00BFC4"))
```

```{r estradiol}
PETC %>% 
  filter(hormone == "estradiol", sex == "female")  %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = sex)) +
  geom_boxplot() + geom_jitter() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  facet_wrap(~study, scales = "free_x") +
  labs(y = "Estradiol (ng/mL)")

@@

```{r progesterone}
PETC %>% 
  filter(hormone == "progesterone")  %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = sex)) +
  geom_boxplot() + geom_jitter() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  facet_wrap(~study, scales = "free_x") +
  labs(y = "Progesterone (ng/mL)") +
  ylim(c(0,6))

@@

```{r cort}
PETC %>% 
  filter(hormone == "cort")  %>% 
ggplot(aes(x = treatment, y = plasma_conc, fill = sex)) +
  geom_boxplot() + geom_jitter() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  facet_wrap(~study, scales = "free_x") +
  labs(y = "Corticosterone (ng/mL)") +
  ylim(c(0,10))
```

@@

a <- ggplot(characterization, aes(x = treatment, y = `Prolactin ng/mL`, fill = sex)) +
  geom_boxplot() + geom_jitter() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        legend.title = element_blank()) +
  labs(subtitle = "Characterization", y = "Prolactin (ng/mL)", x = NULL) +
  #geom_text(data = df, aes(x,y, label = text), color = "darkgrey") +
      ylim(0,120) 
a

@@

e <- manipulation %>%
  ggplot( aes(x = treatment, y = `Prolactin ng/mL`)) +
    geom_boxplot(aes(fill = sex)) + geom_jitter() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "bottom",
          legend.title = element_blank()) +
    ylim(0,125) +
    labs(subtitle = "Manipulation",
       y = "Prolactin (ng/mL)", x = NULL)
e

@@

f <-  prolactin %>%
  filter(treatment %in% c("control", "bldg", "inc_d3", "M_inc3",
                          "inc_d9",  "M_inc9", "inc_d17","M_inc17",
                          "hatch", "M_n2")) %>%
ggplot(aes(x = treatment, y = `Prolactin ng/mL`, fill = Sex)) +
  geom_boxplot(aes(alpha = study)) + geom_jitter() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none") +
  labs(subtitle = "Offspring removed",
       x = NULL) +
  facet_wrap(~sex) +
  annotate("rect", xmin = 2.5, xmax = 4.5, ymin = 0, ymax = 120, alpha = .2) +
    #annotate("rect", xmin = 4.5, xmax = 6.5, ymin = 0, ymax = 120, alpha = .3) +
    annotate("rect", xmin = 6.5, xmax = 8.5, ymin = 0, ymax = 120, alpha = .2) +
    #annotate("rect", xmin = 8.5, xmax = 10.5, ymin = 0, ymax = 120, alpha = .3) +
  ylim(0,120) +
  scale_alpha_manual(values = c(1,0.5))

g <-  prolactin %>%
  filter(treatment %in% c("early","prolong", "extend",
                          "inc_d9","inc_d17","hatch", "n5" )) %>% droplevels() %>%
ggplot(aes(x = treatment, y = `Prolactin ng/mL`, fill = Sex)) +
  geom_boxplot(aes(alpha = study)) + geom_jitter() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none") +
  labs(subtitle = "Timing of transition altered",
       x = NULL, y = NULL) +
  facet_wrap(~sex) +
    annotate("rect", xmin = 4.5, xmax = 7.5, ymin = 0, ymax = 120, alpha = .3) +
  ylim(0,120) +
  scale_alpha_manual(values = c(1,0.5))
